An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-17 draft.tex

\section{Proposed Method} 
\label{method}
This paragraph will be moved to the Proposed Method section - Mario
Based on a reactive architecture \cite{guervos2018introducing} , each
subpopulation is represented as an event message that is pushed asynchronously
into a message queue. Incoming messages trigger stateless functions that receive
the subpopulation and proceed to run an algorithm, using the parameters and
population included in the message. After the specified number of iterations,
each stateless function returns the evolved subpopulation by again pushing a
message to another queue, used for receiving the resulting subpopulations.
Subpopulations are received from the queue by a controller that is responsible
for mixing the individuals from different subpopulations and producing new
subpopulations. These new subpopulations are pushed again by the controller into
the message queue, creating a loop. The cycle stops when the controller receives
a subpopulation containing a candidate solution that satisfies a particular
condition, or a maximum number of messages were received.

\subsection{Event Driven Model} 
\label{edm}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEO}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}

>>>>

\section{Proposed Method} 
\label{method}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEO}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

In this section, we present the design
and a container-based implementation of the model we propose for the execution
of multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mention earlier. As a first step, we describe the general
architecture first, and then we describe each component in detail.

The primary data element used throughout the system is the subpopulation, and at a higher
level, we can view the system as a continuous stream of subpopulations flowing
from one process to the other. By "continuous stream," we mean that ideally,
everything must happen asynchronously without components needing to wait for
others. In this kind of system, this streaming functionality is normally
implemented by using a message queue system. For instance, if one process needs
to communicate a subpopulation to another, it must pack the sub-population into
a message, and then push the message asynchronously to the queuing system; this
means that after the process pushes the message, it continues its execution
without waiting for a result. On the other end, the recipient subscribes to the
message queue by defining an event handler method that is going to be triggered when a
message is pushed to the message queue. The two components at each end of the queue are
Producers that push messages to the queue and Consumers that pull them. This
pattern is an essential component of a reactive architecture because it is
highly scalable; one of the reasons for this are stateless functions. We can
define stateless functions as methods that do not have side effects, meaning
they do not need to read, keep, or modify data outside of the method. If
Consumers are implemented using stateless functions, then there is no difference
netween having one or many copies of the same function pulling work from the queue all at the
same time, because no side effects are going to result from the concurrency.
Based un these general principles we define next the proposed model.

\subsection{Event Driven Model} 
\label{edm}
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure \ref{fig:kafkEO}. Again, we can explain the general model using the analogy
of Producers and Consumers of messages using a queue. First, we can see that
there are two queues, one labeled Input, and the other one Output. In the diagram, 
push operations on a queue are represented by solid arrows connecting to the left side
of the box, and pull or pop operations as solid arrows leaving from the right side.

Based on a reactive architecture \cite{guervos2018introducing} , each
subpopulation is represented as an event message that is pushed asynchronously
into a message queue. Incoming messages trigger stateless functions that receive
the subpopulation and proceed to run an algorithm, using the parameters and
population included in the message. After the specified number of iterations,
each stateless function returns the evolved subpopulation by again pushing a
message to another queue, used for receiving the resulting subpopulations.
Subpopulations are received from the queue by a controller that is responsible
for mixing the individuals from different subpopulations and producing new
subpopulations. These new subpopulations are pushed again by the controller into
the message queue, creating a loop. The cycle stops when the controller receives
a subpopulation containing a candidate solution that satisfies a particular
condition, or a maximum number of messages were received.
